SUPPORTING INFORMATION \\ Determining sequence-dependent DNA oligonucleotide hybridization and dehybridization mechanisms using coarse-grained molecular simulation, Markov state models, and infrared spectroscopy

### 2021-07-30 SI_marked_up.tex
punctuation

\rood{In applying the NN model to each macrostate, we made the simplifying assumption that the ensemble of microstates constituting each macrostate could be represented by a single pattern of Watson-Crick base pairing that are schematically illustrated in Fig.~2a. Indeed, each macrostate is composed of an ensemble of partially frayed states with higher free energy contributions than the intact pattern. However, when averaging across the frayed contributions of all microstates in each macrostate, we have found that in all cases incorporating additional NN configurations changes $\Delta$ F values (relative the corresponding partially frayed H state) by $<$ 1 kJ/mol when compared to using a single microstate. Furthermore, treating termini fraying as complete removal of a nearest neighbor pair is a crude approximation since the model was not intended to incorporate fraying. Given the extent to which a single NN representation captures each macrostate (which is further demonstrated in Fig.~S5), we have elected to maintain a single microstate free energy estimate for each macrostate}

>>>>

\rood{In applying the NN model to each macrostate, we made the simplifying assumption that the ensemble of microstates constituting each macrostate could be represented by a single pattern of Watson-Crick base pairing that are schematically illustrated in Fig.~2a. Indeed, each macrostate is composed of an ensemble of partially frayed states with higher free energy contributions than the intact pattern. However, when averaging across the frayed contributions of all microstates in each macrostate, we have found that in all cases incorporating additional NN configurations changes $\Delta$ F values (relative the corresponding partially frayed H state) by $<$ 1 kJ/mol when compared to using a single microstate. Furthermore, treating termini fraying as complete removal of a nearest neighbor pair is a crude approximation since the model was not intended to incorporate fraying. Given the extent to which a single NN representation captures each macrostate (which is further demonstrated in Fig.~S5), we have elected to maintain a single microstate free energy estimate for each macrostate.}
